Unified Understanding of the Dielectric Nature of Two-Dimensional Materials

### 2018-10-18 paper.tex
Modification for figure 3 main text

\subsection{Universal Relations for 2D Polarizabilities}
\label{sec:first-principles}

@@

Figure \ref{fig-3}c
shows $(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ (in \AA{}) as a
function of $E_{\mathrm{g}}$ (in eV) for the 2D materials
investigated, with a linear regression slope of ~0.166 and $R^{2}$ of
0.84. We observe that materials with lower $E_{\mathrm{g}}$ (<4 eV)
generally lie close to the regression line, while the deviation
becomes greater for materials with $E_{\mathrm{g}}>$4 eV, which has
also been observed in the $E_{\mathrm{b}}-E_{\mathrm{g}}$ relation of
2D materials \cite{Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}. We also
observe that $E_{\mathrm{g}}$ calculated on the HSE06 level shows
better linear correlation with $1/\alpha^{\parallel}$ compared with
the bandgap calculated using the Perdew–Burke–Ernzerhof (PBE) method
(details see Supplementary Information SXX \todo{TBD}). This can be
explained by the fact that the HSE06 hybrid functionals generally have
a better prediction for the bandgap of a material than the PBE method
\todo{some reference?}. It should be noted that although even more
accurate estimation of both $\varepsilon$ and $E_{\mathrm{g}}$ can be
achieved via many-body Green’s function method (GW) together with the
Bethe-Salpeter equation (BSE), the convergence of such method is known
to be highly affected by the dielectric screening of 2D materials
\cite{Hueser_2013_2Dvs3D} (see Supplementary Section SXX
\todo{}). Combining the accuracy, computational effort and
convergence, the choice of the HSE06 hybrid functional may be most
suitable to present the true relationship between $\alpha^{\parallel}$
and $E_{\mathrm{g}}$.

On the other hand, $\alpha^{\perp}$ is observed to be almost
independent of $E_{\mathrm{g}}$. Similar behavior is also observed for
molecular \cite{T_bik_2004} and carbon nanotube \cite{Benedict_1995}
systems when the polarizability is in the direct perpendicular to the
$\pi$ electron cloud. Meanwhile, while $\alpha^{\perp}$ is much
smaller than $\alpha^{\parallel}$, its magnitude can still span over 5
times among different materials, and generally larger for materials
with more atoms in the z-direction (such as Ga$_{2}$S$_{2}$) than
single-atom materials (such as BN). Starting from this observation and
the fact that 2D polarizability has unit of
$4\pi\epsilon\times$[Length], $\alpha^{\perp}$ may actually be related
to a characteristic length in the z-direction of a 2D material. Figure
\ref{fig-3}c shows $\alpha^{\perp}$ as a function of the covalent
thickness $\delta_{\mathrm{2D}}^{\mathrm{cov}}$. The covalent
thickness is defined as the longest distance in the z-direction
between any two atom nuclei plus their covalent radii, such that:
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{2D}}^{\mathrm{cov}} = \mathrm{max}(|z_{i} - z_{j}|
  + r_{i}^{\mathrm{cov}} + r_{j}^{\mathrm{cov}})
\end{equation}
where i, j are two atoms in the 2D material and $r^{\mathrm{cov}}_{i}$
is the covalent radius of atom i, as illustrated in Figure
\ref{fig-delta}. Surprisingly, $\alpha^{\perp}$ shows excellent linear
correlation with $\delta_{\mathrm{2D}}^{\mathrm{cov}}$, with
$R^{2}=0.98$, and a slope very close to $1/4\pi$. In other words, the
quantity $\alpha^{\perp}/\varepsilon_{0}$ can be regarded as the
long-sought-for characteristic thickness of 2D materials. In short, we
have revealed the 2D analog of the Moss relation for both polarization
direction: $\alpha^{\parallel}$ is inversely proportional to the
minimal bandgap $E_{\mathrm{g}}$, while $\alpha^{\perp}$ is the
characteristic thickness of the 2D material. The existence of such
universal scaling relation is confirmed by examining using the
recently-published C2DB database \cite{Haastrup_2018}, with the
dielectric properties of over 200 2D semiconductors calculated on the
PBE level (details see Supplementary Section SXX \todo{TBD}).  We have
further tested the potential relation between the 2D polarizabilities
with other physical quantities, including the effective carrier mass,
quantum capacitance and total atomic polarizabilities while no
apparent correlations are found (details see Supplementary Section SXX
\todo{note}). In the next section, we will show the theoretical
backgrounds of such universal relations of 2D polarizabilities.

>>>>

\subsection{2D Moss Relations}
\label{sec:first-principles}

@@

We now validate Eq. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp}
using the polarizabilities calculated by first principle
calculations. Figure \ref{fig-3}b shows
$(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ (in \AA{}) as a function
of $E_{\mathrm{g}}$ (in eV) for the 2D materials investiaged (circle dots), with a
linear regression slope of ~0.182 and $R^{2}$ of 0.84. From
Ref. \cite{Jiang_2017_Eg_Eb}, the slope between
$(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ and $E_{g}$ is
$8\pi^{2}\varepsilon_{0} \mathrm{\AA}/(eN) \approx 0.436/N$, which
yields $N$ betweem 2 and 3, which is reasonable for the 2D materials
studied. We observe that materials with lower $E_{\mathrm{g}}$ ($<$4
eV) generally lie close to the regression line, while the deviation
becomes greater for materials with $E_{\mathrm{g}}>$4 eV, which has
also been observed in the $E_{\mathrm{b}}-E_{\mathrm{g}}$ relation of
2D materials \cite{Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}. We also
discover that the linearity between
$(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ and $E_{\mathrm{g}}$ is
better when the bandgap is calculated using the HSE06 hybrid
functionals, compared with that from the Perdew--Burk--Ernzerhof (PBE)
exchange correlations (details see Supplementary Section S2 and
Supplementary Figure S5), which can be explained by the fact that the
electronic structure, in particular the bandgap, is generally better
predicted at HSE06 level than PBE level \cite{Heyd_2005}. It should be
noted that although even more accurate estimation of both
$\varepsilon$ and $E_{\mathrm{g}}$ can be achieved via many-body
Green’s function method (GW) together with the Bethe-Salpeter
equation (BSE), the convergence of such method is known to be highly
affected by the dielectric screening of 2D materials
\cite{Hueser_2013_2Dvs3D}. Combining the accuracy, computational
effort and convergence, the choice of the HSE06 hybrid functional may
be most suitable to present the true 2D Moss-like relationship between
$\alpha^{\parallel}$ and $E_{\mathrm{g}}$.

We further examine the relation between $\alpha^{\perp}$ and the
thickness of a 2D material proposed in Eq. \ref{eq:2D-Moss-perp}. Here
we choose the thickness of as 2D material as its ``covalent''
thickness $\delta_{\mathrm{cov}}$, which is
defined as the longest distance along the z-direction between any two
atom nuclei plus their covalent radii:
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{cov}} = \mathrm{max}(|z_{i} - z_{j}|
  + r_{i}^{\mathrm{cov}} + r_{j}^{\mathrm{cov}})
\end{equation}
where i, j are two atoms in the 2D material and $r^{\mathrm{cov}}_{i}$
is the covalent radius of atom i (Figure \ref{fig-3}c). As shown in
Figure \ref{fig-3}b, $\alpha^{\perp}/(4 \pi \varepsilon_{0})$ indeed
shows an excellent linear correlation with $\delta_{\mathrm{cov}}$,
with $R^{2}=0.98$, and the slope very close to $1/4\pi$. In addition
to our theoretical predictions discussed above, the perfect linear
correlation between $\alpha^{\perp}$ and $\delta_{\mathrm{cov}}$ has
its strong physical meaning. Similar to the molecular polarizability
which characterizes the volume of electron cloud of an isolated
molecule \cite{Israelachvili_2011}, the 2D polarizability also
characterizes the volume of the electron cloud of a 2D material per
unit area (from its definition), and naturally represents the
thickness of the electron cloud of the 2D material. The fact that the
thickness of the electron cloud of a 2D material can be approximated
by the extension of valence states in the z-direction, explains the
close match between the linear slope in Figure \ref{fig-3}c and
$1/4\pi$. In other wordst, the universal scaling relation for
$\alpha^{\perp}$ indicates the quantity
$\alpha^{\perp}/\varepsilon_{0}$, is the dielectric characteristic
thickness of a 2D material. We propose that the well-established
experimental protocol for measuring the electronic polarizability of
isolated molecules \cite{Antoine_1999}, can also be extended to
measure $\alpha^{\perp}$ of a 2D material, as a direct estimation of
it thickness, in comparison with the optical ellipsometry techniques
\cite{Weber_2010} widely used to estimate the thickness of 2D
materials, which requires empirical optical model and parameter
fitting.

To rule out the possibility that our conclusion is limited by the
number of materials used, we further validate our proposed 2D
Moss-like relations on the recently-published C2DB database
\cite{Haastrup_2018}, from which we extracted the dielectric
properties of over 230 2D materials calculated at the PBE level, and
overlap them with our results in Figure \ref{fig-3}b and \ref{fig3-c}
(further details see Supplementary Section S3). Althought the
dielectric properties may be overestimated at PBE level due to
underestimation of the bandgap compared with the more accurate HSE06
functionals, apparent linear trends can be observed for both
$\alpha^{\parallel}$ and $\alpha^{\perp}$, with the linear coefficient
very close to the HSE06 results. Therefore, the proposed universal 2D
Moss-like relations are confirmed.  We have also tested the potential
relation between the 2D polarizabilities with other physical
quantities, including the effective carrier mass, quantum capacitance
and total atomic polarizabilities, while no apparent correlations are
found (details see Supplementary Section S3).

In short, we have revealed the 2D analog of the Moss relation for both
polarization direction by using the 2D polarizability: $\alpha^{\parallel}$ is inversely proportional
to the minimal bandgap $E_{\mathrm{g}}$, while $\alpha^{\perp}$ is the
characteristic thickness of the 2D material.
